Scattering from compact objects: \\ Regge poles and the Complex Angular Momentum method

### 2019-12-16 rainbowCAM.tex
The remarks in PDF

%\usepackage[margin=1in]{geometry}
\usepackage{float}
%\usepackage{subfig}
\usepackage{comment}
\usepackage{array}
%\usepackage{varioref}
%\usepackage[hidelinks]{hyperref}
%\usepackage{cleveref}
%\usepackage[numbers]{natbib}
\usepackage{units}
\usepackage{wasysym}
%\usepackage{caption}
%\usepackage{subcaption}
\usepackage{xcolor}

@@

The CAM theory was originally developed to deal theoretically with the propagation and diffraction of radio waves around the Earth, by Watson~\cite{Watson18} (see also the work of Sommerfeld~\cite{Sommerfeld49}). It has since been extensively used in several domains of physics involving resonant scattering theory (see, \textit{e.g.}, Refs.~\cite{deAlfaro:1965zz,Newton:1982qc,Watson18,Sommerfeld49,Nus92,Grandy2000,Uberall1992,AkiRichards2002,AkiRichards2002,Gribov69,
Collins77,BaronePredazzi2002,DonnachieETAL2005} as well as references therein for various applications in quantum mechanics, nuclear physics, electromagnetism, optics, seismology and high energy physics). Since the pioneering work in 1994 by Andersson and Thylwe~\cite{Andersson:1994rk,Andersson:1994rm} the CAM theory has been successfully applied to black hole scattering scenarios. They described the scattering of scalar waves by a Schwarzschild black hole using CAM techniques, and showed that, in this case, the Regge poles are associated with ``surface waves'' localised near the unstable light ring at $ r = 3M $ (\textit{i.e.}, the so-called photon sphere). Later, Decanini, Folacci and Jensen have shown that the complex frequencies of weakly damped QNMs are Breit-Wigner resonances generated by surface waves previously mentioned and, using the concept of Regge trajectories, they were able to construct semiclassically the spectrum of the QNM complex frequencies~\cite{Decanini:2002ha}. Recently, Folacci and Ould~El~Hadj have shown that CAM machinery can be used for precise numerical calculations of scattering cross sections of scalar fields, electromagnetic fields~\cite{Folacci:2019cmc} and gravitational waves~\cite{Folacci:2019vtt} on Schwarzschild space-time. Moreover, using the third WKB approximation to obtain the asymptotic expressions for the lowest Regge poles~\cite{Decanini:2009mu} and associated residues, they have able to provide an analytical approximation describing accurately both ``glory'' and large part of the ``orbiting'' oscillations in black hole scattering cross sections in the short-wavelength regime. An accurate approximation for the black hole absorption cross section has also been derived via an analysis of Regge poles~\cite{Decanini:2011xi,Decanini:2011xw}. In addition, an alternative description of gravitational radiation from black holes based on CAM theory was developed in Ref.~\cite{Folacci:2018sef}.

@@

There is a close relationship between Regge poles and quasi-normal modes (QNMs); both are sets of poles of the scattering matrix, with the latter lying in the complex-frequency plane. The excitation of black hole QNMs leads to distinctive signatures in \emph{time-dependent} scattering scenarios. For example, in the immediate aftermath of a black hole merger, the perturbed black hole returns to a quiescent state via a `ringdown phase' in which its gravitational-wave signal is well described as a sum of quasinormal modes \cite{Giesler:2019uxc}. The QNM spectrum of compact bodies have been well-studied by several authors  \cite{Detweiler:1985zz, Kokkotas:1986gd, Chandrasekhar449, Kokkotas:1992ka, Leins:1993zz, Andersson:1995ez, Andersson1996}, and are reviewed in Ref.~\cite{Kokkotas:1999bd}.

It was recently shown \cite{Dolan:2017rtj, Stratton:2019deq} that time-independent scattering by compact bodies generates (in principle) a \emph{rainbow scattering} phenomenon in the short wavelength regime ($M \omega \gg 1$). The rainbow scattering phenomenon is linked to the formation of a cusp caustic in the incident wavefront (see Fig.~1 in Ref.~\cite{Stratton:2019deq}), and to the stationary point in the geodesic deflection function associated with a ray (that is, a null geodesic) that passes somewhat inside the body. For less-dense bodies, such as stars and white dwarfs, the cusp caustic forms at a distance $d \sim R^2 / (4M)$ downstream of the body, and the rainbow angle is $\theta_r \sim 4M/R$ (e.g.~for the Sun, $d \approx 550 \, \text{a.u.}$ and $\theta_r \approx 1.8 \, \text{arcsec}$) \footnote{The rainbow angle $\theta_r \approx 4M/R$ is distinct from the Einstein ring angle of $\theta_E \approx \sqrt{4M/r}$}. For compact bodies such as neutron stars, however, the cusp caustic forms near the surface of the body, and the rainbow angle is large ($\theta_r \gtrsim 59.6^\circ$ for $R/M = 6$; see Table I in Ref.~\cite{Stratton:2019deq}). In this case, the rainbow angle is -- in principle at least -- a useful diagnostic of the matter distribution within the body and thus its nuclear equation of state.

@@

The remainder of this paper is organised as follows. Sec.~\ref{SecII} reviews the theory of scalar waves on a spherically-symmetric spacetime of a compact object. Here we describe our model spacetime (\ref{SecIIa}), the effective potentials for wave scattering (\ref{subsec:Potentials}) and the physical boundary conditions that define the S-matrix (\ref{subsec:bc}). Sec.~\ref{sec:RP} focusses on the Regge pole spectrum. Here we outline the link between Regge poles and QNMs (\ref{subsec:QNMs_RPs}), we describe the numerical method (\ref{subsec:method}), and we present new numerical results for the spectrum (\ref{subsec:results1}) which exhibits three distinct branches of Regge poles (see e.g.~Fig.~\ref{RP_R226_approx_2Mw_3_6_s_1}); in Sec.~\ref{subsec:WKB} we apply the WKB method to obtain an approximate formula for the `broad resonance' branch. Sec.~\ref{sec:CAM} concerns the application of CAM techniques to the calculation of the scattering cross section. Here we review the standard partial-wave expansion of the scattering amplitude (\ref{subsec:partial}), we apply CAM techniques to write this as the sum of a residue series and a background integral (\ref{SecIIc}), and we present a selection of numerical results for $d\sigma/d\Omega$ (\ref{subsec:results2}). We conclude with a discussion in Sec.~\ref{sec:conclusions}.

@@

We do not use the gaussian elimination step. Instead we find solutions of \eqref{Recurrence_4_terms} by adapting the \textit{Hill determinant approach} employed by Majumdar and Panchapakesan~\cite{mp} to solve the black hole recurrence formula of Leaver \cite{Leaver:1985ax}. The nontrivial solutions of \eqref{Recurrence_4_terms} exist when the Hill determinant vanishes:
\begin{equation}
\label{Determinant_Hill_4_termes}
D   =  \begin{vmatrix}
   \beta_0         &  \alpha_0    &        0             &       0                    &          0                &     \ldots          &     \ldots        &    \ldots \\
   \gamma_1        &  \beta_1      &     \alpha_1     &       0                    &          0                &     \ldots          &     \ldots        &    \ldots  \\
    \delta_2       &   \gamma_2     &    \beta_2       &   \alpha_2             &         0                &     \ldots           &    \ldots         &    \ldots  \\
    \vdots         &      \ddots     &     \ddots       &    \ddots                &       \ddots          &     \ddots           &   \ldots          &    \ldots \\
     \vdots        &     \vdots      &     \delta_{n-1}      &    \gamma_{n-1}      &     \beta_{n-1}     &      \alpha_{n-1} &    \ddots         &    \ldots  \\
     \vdots        &  \vdots        &     \vdots        &     \delta_n                &    \gamma_{n}    &     \beta_{n}        &     \alpha_{n}  &    \ddots     \\
     \vdots        &  \vdots        &     \vdots        &     \vdots                &    \ddots            &     \ddots            &     \ddots       &    \ddots
                        \end{vmatrix}
       = 0.
\end{equation}
%
Letting $D_n$ be the determinant of the $n \times n$ sub matrix of $D$ (with diagonal $\{\beta_0,\beta_1,....\beta_n\}$), by \eqref{Recurrence_4_terms}
%
\begin{equation}
\label{derecurrence_4_termes}
D_n=\beta_n D_{n-1} - \gamma_{n}\alpha_{n-1}D_{n-2} + \delta_n \alpha_{n-1} \alpha_{n-2} D_{n-3}
\end{equation}
%
with the initial conditions
 \begin{equation}
 \label{Determinant_initial_conds}
 \begin{split}
    D_0 &=\beta_0, \\
    D_1 &=\beta_1\beta_0-\gamma_1\alpha_0  \\
    D_2 &=\beta_0(\beta_1 \beta_2 - \alpha_1 \gamma_2)- \alpha_0(\alpha_1 \delta_2 -\gamma_1 \beta_2)
 \end{split}
 \end{equation}
%
Regge poles (QNM frequencies) are found by fixing $\omega$ ($\lambda$) and numerically finding roots $\lambda_n$ ($\omega_n$) of $D_n$, i.e.~ $D_n(\lambda_n,\omega)=0$ ($D_n(\lambda,\omega_n)=0$).
%Regge poles $\lambda_n$ (QNM frequencies $\omega_n$) are roots of $D_n$

@@

Due to the long rang nature of the field propagating on the Schwarzschild BH (outside the compact body), the scattering amplitude~\eqref{Scalar_Scattering_amp} and the background integral~\eqref{CAM_Scalar_Scattering_amp_decomp_Background_a} both suffer a lack of convergence. To overcome this problem, i.e., to accelerate the convergence of this sum and integral, we have used the method described in the Appendix of Ref~\cite{Folacci:2019cmc}. We have performed all the numerical calculations by using {\it Mathematica}. % \cite{Mathematica}.

@@

\begin{figure*}[htp!]
 \includegraphics[scale=0.50]{Scattering_Cross_Section_R_6_2Mw_3}
  \vspace*{-0.3cm}
\caption{\label{S_0_R_6_2Mw_3_Exact_vs_CAM} The scalar cross section of a compact bodies for $2M\omega=3$ and $R=6M$, its Regge pole approximation and the background integral contribution. The plots show the effect of including successively more Regge poles (plots 1--3). In the final plot, the background integral is added, giving a cross section which agrees well with the (regularized) partial-wave sum.}
\end{figure*}

\begin{figure*}[htp!]
 \includegraphics[scale=0.50]{Scattering_Cross_Section_R_6_2Mw_16}
 \vspace*{-0.3cm}
\caption{\label{S_0_R_6_2Mw_16_Exact_vs_CAM} The scalar cross section of a compact bodies for $2M\omega=16$ and $R=6M$, its Regge pole approximation and the background integral contribution. The plots show the effect of including successively more Regge poles (plots 1--3). In the final plot, the background integral is added, giving a cross section which agrees well with the (regularized) partial-wave sum.}
\end{figure*}

\begin{figure*}[htp]
\centering
 \includegraphics[scale=0.50]{Scattering_Cross_Section_R_2-dot-26_2Mw_3}
  \vspace*{-0.3cm}
\caption{\label{S_0_R_2-dot-26_2Mw_3_Exact_vs_CAM} The scalar cross section of an ultra-compact body for $2M\omega=3$ and $R=2.26M$ and its Regge pole approximation.  The plots show the effect of including successively more Regge poles (plots 1--3). In the final plot, the sum over Regge poles gives a cross section which agrees well with the (regularized) partial-wave sum for intermediate and large values of the scattering angle.}
\end{figure*}

\begin{figure*}[htp]
\centering
 \includegraphics[scale=0.50]{Scattering_Cross_Section_R_2-dot-26_2Mw_6}
  \vspace*{-0.3cm}
\caption{\label{S_0_R_2-dot-26_2Mw_6_Exact_vs_CAM} The scalar cross section of an ultra-compact body for $2M\omega=6$ and $R=2.26M$ and its Regge pole approximation. The plots show the effect of including successively more Regge poles (plots 1--3). In the final plot, the sum over Regge poles gives a cross section which agrees well with the (regularized) partial-wave sum for intermediate and large values of the scattering angle.}
\end{figure*}

\begin{figure}[htp]
\centering
 \includegraphics[scale=0.50]{Rainbow_Cross_Section_R_6_2Mw_16}
  \vspace*{-0.3cm}
\caption{\label{Rainbow_Cross_Section_R_6_2Mw_16} Rainbow scattering for compact bodies for $2M\omega=16$ and $R=6M$, its Regge pole approximation and different contributions of the sum over Regge poles.}
\end{figure}

\begin{figure}[htp]
\centering
 \includegraphics[scale=0.50]{Diff_Contribution_Cross_Section_R_2-dot-26_2Mw_6}
  \vspace*{-0.3cm}
\caption{\label{Diff_Contribution_Cross_Section_R_2-dot-26_2Mw_6} Rainbow scattering for compact bodies for $2M\omega=16$ and $R=2.26M$, its Regge pole approximation and different contributions of the sum over Regge poles.}
\end{figure}

@@

Figure \ref{S_0_R_6_2Mw_3_Exact_vs_CAM} demonstrates that the CAM cross section approaches the partial-wave cross section as (i) successively more Regge poles are included in the sum (\ref{CAM_Scalar_Scattering_amp_decomp_RP}), and (ii) the background-integral contributions (\ref{CAM_Scalar_Scattering_amp_decomp_Background}) are included. The first plot shows that, at a `low' frequency of $M \omega = 3/2$ for the neutron star model ($R/M = 6$), taking a sum over just \emph{two} Regge poles in Eq.~(\ref{CAM_Scalar_Scattering_amp_decomp_RP}) captures the crude features of the cross section. The final plot shows that a cross section calculated from a sum of $15$ Regge poles and the background integral is indistinguishable (on the plot) from the partial-wave sum.

@@

Figure \ref{S_0_R_2-dot-26_2Mw_3_Exact_vs_CAM} shows the cross section for an Ultra Compact Object with $R/M = 2.26$ at the `low' frequency of $M \omega = 3/2$. In this case, the rainbow angle exceeds $180^\circ$, and there is both a light-ring and a trapping region (see Fig.~\ref{fig:Veff}). The cross section exhibits regular orbiting oscillations with angle $\theta$. The angular width is consistent with generation by the light-ring (i.e.~ the peak in the potential barrier). The second plot shows that including just 3 modes from each of the three branches leads to a good description of scattering at large angles $\theta \gtrsim 100^\circ$. As there is no shadow region in this case, the cross section at large angles in non-negligible. For $R/M = 2.26$, the cross section at the antipodal point ($\theta = 180^\circ$) is a factor of $> 10^6$ larger than in the $R/M = 6$ case. The final plot shows that excellent agreement with the partial-wave results is obtained, for $\theta \gtrsim 20^\circ$, by summing over $27$ poles.

@@

The spectrum of Regge poles exhibits two distinct branches of poles in the neutron star case $R/M = 6$ (see Fig.~\ref{RP_R6_approx_2Mw_3_6_s_1}), which we have labelled `broad resonances' and `surface waves'. Ultra-compact objects have, in addition, a third branch of `narrow resonances' (see Fig.~\ref{RP_R226_approx_2Mw_3_6_s_1}), linked to the existence of an effective cavity between the light-ring and the object's surface. Similar branches of poles arise in scattering by a transparent sphere, and so it is natural to adopt the terminology used to describe these branches in Mie scattering \cite{Nussenzveig:2006}.

@@

The CAM toolkit was applied here to gain a complementary practical method for calculating scattering amplitudes. However, in its current form, the method is not particularly efficient, for two reasons; first, it requires the computation of a background integral in addition to residue sum; and second, the poles on the broad-resonance branch have an approximately uniform spacing, $\Delta \lambda \sim 2$, and thus a large number of poles must be calculated. In the black-hole case, by contrast, there is only a single branch of surface-wave-type modes (see Fig.~\ref{RP_R6_approx_2Mw_3_6_s_1}), and in the high-frequency limit, a single pole captures both the orbiting and glory phenomena \cite{Folacci:2019cmc, Folacci:2019vtt}. In the case of Mie scattering, a powerful extension of the CAM approach is to define the so-called Regge-Debye poles \cite{Nussenzveig:2006}, thereby eliminating the surface-wave branch entirely. This is a possible direction for future investigation.

>>>>

%\usepackage[margin=1in]{geometry}
\usepackage{float}
%\usepackage{subfig}
\usepackage{comment}
\usepackage{array}
%\usepackage{varioref}
%\usepackage[hidelinks]{hyperref}
%\usepackage{cleveref}
%\usepackage[numbers]{natbib}
\usepackage{units}
\usepackage{wasysym}
%\usepackage{caption}
%\usepackage{subcaption}
\usepackage{xcolor}
\usepackage{soul}

@@

The CAM theory was originally developed to deal theoretically with the propagation and diffraction of radio waves around the Earth, by Watson~\cite{Watson18} (see also the work of Sommerfeld~\cite{Sommerfeld49}). It has since been extensively used in several domains of physics involving resonant scattering theory (see, e.g., Refs.~\cite{deAlfaro:1965zz,Newton:1982qc,Watson18,Sommerfeld49,Nussenzveig:2006,Grandy2000,Uberall1992,AkiRichards2002,AkiRichards2002,Gribov69,
Collins77,BaronePredazzi2002,DonnachieETAL2005} as well as references therein for various applications in quantum mechanics, nuclear physics, electromagnetism, optics, seismology and high energy physics). Since the pioneering work in 1994 by Andersson and Thylwe~\cite{Andersson:1994rk,Andersson:1994rm} the CAM theory has been successfully applied to black hole scattering scenarios. They described the scattering of scalar waves by a Schwarzschild black hole using CAM techniques, and showed that, in this case, the Regge poles are associated with ``surface waves'' localised near the unstable light ring at $ r = 3M $ (\textit{i.e.}, the so-called photon sphere). Later, Decanini, Folacci and Jensen have shown that the complex frequencies of weakly damped QNMs are Breit-Wigner resonances generated by surface waves previously mentioned and, using the concept of Regge trajectories, they were able to construct semiclassically the spectrum of the QNM complex frequencies~\cite{Decanini:2002ha}. Recently, Folacci and Ould~El~Hadj have shown that CAM machinery can be used for precise numerical calculations of scattering cross sections of scalar fields, electromagnetic fields~\cite{Folacci:2019cmc} and gravitational waves~\cite{Folacci:2019vtt} on Schwarzschild space-time. Moreover, using the third WKB approximation to obtain the asymptotic expressions for the lowest Regge poles~\cite{Decanini:2009mu} and associated residues, they have able to provide an analytical approximation describing accurately both ``glory'' and large part of the ``orbiting'' oscillations in black hole scattering cross sections in the short-wavelength regime. An accurate approximation for the black hole absorption cross section has also been derived via an analysis of Regge poles~\cite{Decanini:2011xi,Decanini:2011xw}. In addition, an alternative description of gravitational radiation from black holes based on CAM theory was developed in Ref.~\cite{Folacci:2018sef}.

@@

There is a close relationship between Regge poles and quasi-normal modes (QNMs); both are sets of poles of the scattering matrix, with the latter lying in the complex-frequency plane. The excitation of black hole QNMs leads to distinctive signatures in \emph{time-dependent} scattering scenarios. For example, in the immediate aftermath of a black hole merger, the perturbed black hole returns to a quiescent state via a ``ringdown phase'' in which its gravitational-wave signal is well described as a sum of quasinormal modes \cite{Giesler:2019uxc}. The QNM spectrum of compact bodies have been well-studied by several authors  \cite{Detweiler:1985zz, Kokkotas:1986gd, Chandrasekhar449, Kokkotas:1992ka, Leins:1993zz, Andersson:1995ez, Andersson1996}, and are reviewed in Ref.~\cite{Kokkotas:1999bd}.

%It was recently shown \cite{Dolan:2017rtj, Stratton:2019deq} that time-independent scattering by compact bodies generates (in principle) a \emph{rainbow scattering} phenomenon in the short wavelength regime ($M \omega \gg 1$). The rainbow scattering phenomenon is linked to the formation of a cusp caustic in the incident wavefront (see Fig.~1 in Ref.~\cite{Stratton:2019deq}), and to the stationary point in the geodesic deflection function associated with a ray (that is, a null geodesic) that passes somewhat inside the body. For less-dense bodies, such as stars and white dwarfs, the cusp caustic forms at a distance $d \sim R^2 / (4M)$ downstream of the body, and the rainbow angle is $\theta_r \sim 4M/R$ (e.g.~for the Sun, $d \approx 550 \, \text{a.u.}$ and $\theta_r \approx 1.8 \, \text{arcsec}$) \footnote{The rainbow angle $\theta_r \approx 4M/R$ is distinct from the Einstein ring angle of $\theta_E \approx \sqrt{4M/r}$}. For compact bodies such as neutron stars, however, the cusp caustic forms near the surface of the body, and the rainbow angle is large ($\theta_r \gtrsim 59.6^\circ$ for $R/M = 6$; see Table I in Ref.~\cite{Stratton:2019deq}). In this case, the rainbow angle is -- in principle at least -- a useful diagnostic of the matter distribution within the body and thus its nuclear equation of state.

\moh{Remark for Tom and Sam : In the following paragraph : Render unto Caesar the things that are Caesar's}\\

Stratton and Dolan have recently shown that time-independent scattering by compact bodies generates (in principle) a \emph{rainbow scattering} phenomenon in the short wavelength regime ($M \omega \gg 1$)~\cite{Dolan:2017rtj, Stratton:2019deq}. The rainbow scattering phenomenon is linked to the formation of a cusp caustic in the incident wavefront (see Fig.~1 in Ref.~\cite{Stratton:2019deq}), and to the stationary point in the geodesic deflection function associated with a ray (that is, a null geodesic) that passes somewhat inside the body. For less-dense bodies, such as stars and white dwarfs, the cusp caustic forms at a distance $d \sim R^2 / (4M)$ downstream of the body, and the rainbow angle is $\theta_r \sim 4M/R$ (e.g.~for the Sun, $d \approx 550 \, \text{a.u.}$ and $\theta_r \approx 1.8 \, \text{arcsec}$) \footnote{The rainbow angle $\theta_r \approx 4M/R$ is distinct from the Einstein ring angle of $\theta_E \approx \sqrt{4M/r}$}. For compact bodies such as neutron stars, however, the cusp caustic forms near the surface of the body, and the rainbow angle is large ($\theta_r \gtrsim 59.6^\circ$ for $R/M = 6$; see Table I in Ref.~\cite{Stratton:2019deq}). In this case, the rainbow angle is -- in principle at least -- a useful diagnostic of the matter distribution within the body and thus its nuclear equation of state.

@@

The remainder of this paper is organised as follows. Sec.~\ref{SecII} reviews the theory of scalar waves on a spherically-symmetric spacetime of a compact object. Here we describe our model spacetime (\ref{SecIIa}), the effective potentials for wave scattering (\ref{subsec:Potentials}) and the physical boundary conditions that define the S-matrix (\ref{subsec:bc}). Sec.~\ref{sec:RP} focusses on the Regge pole spectrum. Here we outline the link between Regge poles and QNMs (\ref{subsec:QNMs_RPs}), we describe the numerical method (\ref{subsec:method}), and we present new numerical results for the spectrum (\ref{subsec:results1}) which exhibits three distinct branches of Regge poles (see e.g.~Fig.~\ref{RP_R226_approx_2Mw_3_6_s_1}); in Sec.~\ref{subsec:WKB} we apply the WKB method to obtain an approximate formula for the ``broad resonance'' branch. Sec.~\ref{sec:CAM} concerns the application of CAM techniques to the calculation of the scattering cross section. Here we review the standard partial-wave expansion of the scattering amplitude (\ref{subsec:partial}), we apply CAM techniques to write this as the sum of a residue series and a background integral (\ref{SecIIc}), and we present a selection of numerical results for $d\sigma/d\Omega$ (\ref{subsec:results2}). We conclude with a discussion in Sec.~\ref{sec:conclusions}.

@@

We do not use the gaussian elimination step. Instead we find solutions of \eqref{Recurrence_4_terms} by adapting the \textit{Hill determinant approach} employed by Majumdar and Panchapakesan~\cite{mp} to solve the black hole recurrence formula of Leaver \cite{Leaver:1985ax}. The nontrivial solutions of \eqref{Recurrence_4_terms} exist when the Hill determinant vanishes:
\begin{equation}
\label{Determinant_Hill_4_termes}
D   =  \begin{vmatrix}
   \beta_0         &  \alpha_0    &        0             &       0                    &          0                &     \ldots          &     \ldots        &    \ldots \\
   \gamma_1        &  \beta_1      &     \alpha_1     &       0                    &          0                &     \ldots          &     \ldots        &    \ldots  \\
    \delta_2       &   \gamma_2     &    \beta_2       &   \alpha_2             &         0                &     \ldots           &    \ldots         &    \ldots  \\
    \vdots         &      \ddots     &     \ddots       &    \ddots                &       \ddots          &     \ddots           &   \ldots          &    \ldots \\
     \vdots        &     \vdots      &     \delta_{n-1}      &    \gamma_{n-1}      &     \beta_{n-1}     &      \alpha_{n-1} &    \ddots         &    \ldots  \\
     \vdots        &  \vdots        &     \vdots        &     \delta_n                &    \gamma_{n}    &     \beta_{n}        &     \alpha_{n}  &    \ddots     \\
     \vdots        &  \vdots        &     \vdots        &     \vdots                &    \ddots            &     \ddots            &     \ddots       &    \ddots
                        \end{vmatrix}
       = 0.
\end{equation}
%
Letting $D_n$ be the determinant of the $n \times n$ sub matrix of $D$ (with diagonal $\{\beta_0,\beta_1,....\beta_n\}$), by \eqref{Recurrence_4_terms}
%
\begin{equation}
\label{derecurrence_4_termes}
D_n=\beta_n D_{n-1} - \gamma_{n}\alpha_{n-1}D_{n-2} + \delta_n \alpha_{n-1} \alpha_{n-2} D_{n-3}
\end{equation}
%
with the initial conditions
 \begin{equation}
 \label{Determinant_initial_conds}
 \begin{split}
    D_0 &=\beta_0, \\
    D_1 &=\beta_1\beta_0-\gamma_1\alpha_0  \\
    D_2 &=\beta_0(\beta_1 \beta_2 - \alpha_1 \gamma_2)- \alpha_0(\alpha_1 \delta_2 -\gamma_1 \beta_2)
 \end{split}
 \end{equation}
%
Or equivalently \moh{we can also use this forme}
\begin{align}
\label{recurrence_Hill_RN_4_termes}
D_n    & =\left(\prod_{k=1}^{n+1} k^2\right) P_{n+1} \nonumber\\
       &  = 1\times 2^2 \ldots (n-2)^2(n-1)^2n^2(n+1)^2 P_{n+1},
\end{align}
where
\begin{eqnarray}
\label{recurrence_Hill_RN_4_termes_bis}
% \nonumber % Remove numbering (before each equation)
P_n = & & \left(\frac{\beta_{n-1}}{n^2}\right)P_{n-1}-\left(\frac{\gamma_{n-1}}{n^2}\right)\left(\frac{\alpha_{n-2}}{(n-1)^2}\right)P_{n-2} \nonumber \\
  &+& \left(\frac{\delta_{n-1}}{n^2}\right) \left(\frac{\alpha_{n-2}}{(n-1)^2}\right) \left(\frac{\alpha_{n-3}}{(n-2)^2}\right) P_{n-3}
\end{eqnarray}
with the initial conditions
 \begin{equation}
 \begin{split}
    P_1&=\beta_0\\
    P_2&=\frac{\beta_0\beta_1-\gamma_1\alpha_0}{4} \\
    P_3&=\frac{\beta_0(\beta_1 \beta_2 - \alpha_1 \gamma_2)- \alpha_0(\alpha_1 \delta_2 -\gamma_1 \beta_2)}{36}
 \end{split}
 \end{equation}

Regge poles (QNM frequencies) are found by fixing $\omega$ ($\lambda$) and numerically finding roots $\lambda_n$ ($\omega_n$) of $D_n$, i.e.~ $D_n(\lambda_n,\omega)=0$ ($D_n(\lambda,\omega_n)=0$).
%Regge poles $\lambda_n$ (QNM frequencies $\omega_n$) are roots of $D_n$

@@

Due to the long rang nature of the field propagating on the Schwarzschild BH (outside the compact body), the scattering amplitude~\eqref{Scalar_Scattering_amp} and the background integral~\eqref{CAM_Scalar_Scattering_amp_decomp_Background_a} both suffer a lack of convergence. To overcome this problem, \textit{i.e.}, to accelerate the convergence of this sum and integral, we have used the method described in the Appendix of Ref~\cite{Folacci:2019cmc}. We have performed all the numerical calculations by using {\it Mathematica}. % \cite{Mathematica}.

@@

\begin{figure*}[htp!]
 \includegraphics[scale=0.50]{Scattering_Cross_Section_R_6_2Mw_3}
  \vspace*{-0.35cm}
\caption{\label{S_0_R_6_2Mw_3_Exact_vs_CAM} The scalar cross section of a compact bodies for $2M\omega=3$ and $R=6M$, its Regge pole approximation and the background integral contribution. The plots show the effect of including successively more Regge poles (plots 1--3). In the final plot, the background integral is added, giving a cross section which agrees well with the (regularized) partial-wave sum.}
\end{figure*}

\begin{figure*}[htp!]
 \includegraphics[scale=0.50]{Scattering_Cross_Section_R_6_2Mw_16}
 \vspace*{-0.35cm}
\caption{\label{S_0_R_6_2Mw_16_Exact_vs_CAM} The scalar cross section of a compact bodies for $2M\omega=16$ and $R=6M$, its Regge pole approximation and the background integral contribution. The plots show the effect of including successively more Regge poles (plots 1--3). In the final plot, the background integral is added, giving a cross section which agrees well with the (regularized) partial-wave sum.}
\end{figure*}

\begin{figure*}[htp!]
\centering
 \includegraphics[scale=0.50]{Scattering_Cross_Section_R_2-dot-26_2Mw_3}
  \vspace*{-0.45cm}
\caption{\label{S_0_R_2-dot-26_2Mw_3_Exact_vs_CAM} The scalar cross section of an UCOs for $2M\omega=3$ and $R=2.26M$ and its Regge pole approximation. The plots show the effect of including successively more Regge poles (plots 1--3). In the final plot, the sum over Regge poles gives a cross section which agrees well with the (regularized) partial-wave sum for intermediate and large values of the scattering angle.}
\end{figure*}

\begin{figure*}[htp!]
\centering
 \includegraphics[scale=0.50]{Scattering_Cross_Section_R_2-dot-26_2Mw_6}
  \vspace*{-0.45cm}
\caption{\label{S_0_R_2-dot-26_2Mw_6_Exact_vs_CAM} The scalar cross section of an UCOs for $2M\omega=6$ and $R=2.26M$ and its Regge pole approximation. The plots show the effect of including successively more Regge poles (plots 1--3). In the final plot, the sum over Regge poles gives a cross section which agrees well with the (regularized) partial-wave sum for intermediate and large values of the scattering angle.}
\end{figure*}

\begin{figure}[htp!]
\centering
 \includegraphics[scale=0.50]{Rainbow_Cross_Section_R_6_2Mw_16}
  \vspace*{-0.45cm}
\caption{\label{Rainbow_Cross_Section_R_6_2Mw_16} Rainbow scattering for compact bodies for $2M\omega=16$ and $R=6M$, its Regge pole approximation and different contributions of the sum over Regge poles.}
\end{figure}

\begin{figure}[htp!]
\centering
 \includegraphics[scale=0.50]{Diff_Contribution_Cross_Section_R_2-dot-26_2Mw_6}
  \vspace*{-0.45cm}
\caption{\label{Diff_Contribution_Cross_Section_R_2-dot-26_2Mw_6} Rainbow scattering for UCOs for $2M\omega=16$ and $R=2.26M$, its Regge pole approximation and different contributions of the sum over Regge poles.}
\end{figure}

@@

Figure \ref{S_0_R_6_2Mw_3_Exact_vs_CAM} demonstrates that the CAM cross section approaches the partial-wave cross section as (i) successively more Regge poles are included in the sum (\ref{CAM_Scalar_Scattering_amp_decomp_RP}), and (ii) the background-integral contributions (\ref{CAM_Scalar_Scattering_amp_decomp_Background}) are included. The first plot shows that, at a ``low'' frequency of $M \omega = 3/2$ for the neutron star model ($R/M = 6$), taking a sum over just \emph{two} Regge poles in Eq.~(\ref{CAM_Scalar_Scattering_amp_decomp_RP}) captures the crude features of the cross section. The final plot shows that a cross section calculated from a sum of $15$ Regge poles and the background integral is indistinguishable (on the plot) from the partial-wave sum.

@@

Figure \ref{S_0_R_2-dot-26_2Mw_3_Exact_vs_CAM} shows the cross section for an Ultra Compact Object with $R/M = 2.26$ at the ``low'' frequency of $M \omega = 3/2$. In this case, the rainbow angle exceeds $180^\circ$, and there is both a light-ring and a trapping region (see Fig.~\ref{fig:Veff}). The cross section exhibits regular orbiting oscillations with angle $\theta$. The angular width is consistent with generation by the light-ring (i.e.~ the peak in the potential barrier). The second plot shows that including just 3 modes from each of the three branches leads to a good description of scattering at large angles $\theta \gtrsim 100^\circ$. As there is no shadow region in this case, the cross section at large angles in non-negligible. For $R/M = 2.26$, the cross section at the antipodal point ($\theta = 180^\circ$) is a factor of $> 10^6$ larger than in the $R/M = 6$ case. The final plot shows that excellent agreement with the partial-wave results is obtained, for $\theta \gtrsim 20^\circ$, by summing over $27$ poles.

@@

The spectrum of Regge poles exhibits two distinct branches of poles in the neutron star case $R/M = 6$ (see Fig.~\ref{RP_R6_approx_2Mw_3_6_s_1}), which we have labelled ``broad resonances'' and ``surface waves''. Ultra-compact objects have, in addition, a third branch of ``narrow resonances'' (see Fig.~\ref{RP_R226_approx_2Mw_3_6_s_1}), linked to the existence of an effective cavity between the light-ring and the object's surface. Similar branches of poles arise in scattering by a transparent sphere, and so it is natural to adopt the terminology used to describe these branches in Mie scattering \cite{Nussenzveig:2006}.

@@

\moh{I propose this following paragraph in summary}\\

%The CAM toolkit was applied here to gain a complementary practical method for calculating scattering amplitudes. However, in its current form, the method is not particularly efficient, for two reasons; first, it requires the computation of a background integral in addition to residue sum; and second, the poles on the broad-resonance branch have an approximately uniform spacing, $\Delta \lambda \sim 2$, and thus a large number of poles must be calculated. In the black-hole case, by contrast, there is only a single branch of surface-wave-type modes (see Fig.~\ref{RP_R6_approx_2Mw_3_6_s_1}), and in the high-frequency limit, a single pole captures both the orbiting and glory phenomena \cite{Folacci:2019cmc, Folacci:2019vtt}. In the case of Mie scattering, a powerful extension of the CAM approach is to define the so-called Regge-Debye poles \cite{Nussenzveig:2006}, thereby eliminating the surface-wave branch entirely. This is a possible direction for future investigation.
